---
title: "Array in R Notebook"
output: html_notebook
---

#### **What is array in R programming?**

##### An array is a data structure that can hold multi-dimensional data. In R, the array is objects that can hold two or more than two-dimensional data. For example, in square matrices can contain two rows and two columns and dimension can take five.
##### to create an array we will be using array() function. this wil take vector as put to create an array.

more than 2D array can be created with dim parameter. 
array() (2,3,4) --> this specifies that there 4 arrays of 2,3

##### **Syntex for creating array**

 **array_name <- array(data, dim = ())**


```{r}
v1 <- c(1,4,5)
v2 <- c(10,20,30,40,50,60)
v3 <- array(c(v1,v2), dim = c(3,3,2))
print(v3)


```

**If sequence is not working properly then how to handel this scenario**
```{r}
v1 <- c(1,4,5)
v2 <- c(10,20,30,40,50,60,70,80)
v3 <- array(c(v1,v2), dim = c(3,3,4))
print(v3)

```
---
Above two outputs are different. Since there were few elements were left as per specified dimesion so next array started from elements which was left in the previous array.
---



##### **Naming Convention in Matrix**

```{r}
col_name <- c("c1", "c2", "c3")
row_name <- c("r1", "r2", "r3")
mat_name <- c("mat1", "mat2", "mat3", "mat4")

v4 <- array(c(v1,v2), dim = c(3,3,4), dimnames <- list(row_name, col_name, mat_name) )
print(v4)

```

##### **if number of elemenent in matrix name and number of matrix in dimensions are not same then above code will give error and array will not be created.**

```{r}
print(v4[3,,2])

print(v4[3,2,2])

print(v4[,2,2])
```
---
output:
  pdf_document:
    highlight: tango
    
##### **v4[r,c,m] here r --> row #, c --> column # and m --> matrix numbber**

##### *oprations of matrix*
---


```{r}
v5 <- v4+v3
print (v4)
print(v3)
print(v5)
```


