---
title: "List in R Data statucture"
output: html_notebook
---

#### Definitin of List in R
A list in R is a generic object consisting of an ordered collection of objects. **Lists are one-dimensional, heterogeneous data structures.** The list can be a list of vectors, a list of matrices, a list of characters and a list of functions, and so on.

**A list is actually still a vector in R, but it's not an atomic vector. We construct a list explicitly with list() but, like atomic vectors, most lists are created some other way in real life.**

we use c() to create a vector but to create a list we use list() in r

##### **Lets create list with vector**


```{r}
# lets create a vector

vec <- c(8,9,10)
char_vec <- c("ram", "shyam", "lala", "kala")
logic_vec <- c(TRUE, FALSE, TRUE)

list1 <- list(vec, char_vec, logic_vec)
list1
```

##### **Lets create list method 2**
```{r}
list2 <- list(1,2,3,4,5, "ram", "shyam", c(9,8,7), 52L, 86,7)
list2
```

##### **Naming of List**

```{r}
list3 <- list(c("ram", "mohan", "sohan"), c(56,89,78), list("btech", "bsc", "ba"))
list3

names(list3) <- c("student", "marks", "courses")

list3

```
##### **Accessing the list**

```{r}

```

